---
title: "How to obtain personalised updates from EU Clinical Trials Register"
author: "Ralf Herold"
date: "`r file.info('howto.Rmd')$mtime`"
output: html_document
params: 
  output_dir = "`r getwd ()`"

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
# command line set up:
# git remote add origin https://github.com/rfhb/euctrnotifications.git
# git pull -u origin master
# git push -u origin master
```

# Objective

The purpose of this document is to describe how a user can set up personalised notifications to obtain updates on clinical trials of interest. This is based on protocol-related information that is made publicly available in the EU Clinical Trials Register [EUCTR](https://www.clinicaltrialsregister.eu/). The licence of this document (Apache 2.0) can be found [here](https://github.com/rfhb/euctrnotifications/blob/master/LICENSE).

```{r cars}
summary(cars)
```

# Overview

Also diagrammes will be included into the how to. 

```{r overviewdiagram, fig.height=10}
suppressWarnings({
  library(DiagrammeR, verbose = FALSE)
})

grViz('
digraph overview {
  # this does not follow a particular 
  # graphic methodology but just 
  # collects the elements 

  graph [overlap = true, fontsize = 10]

  node [shape = parallelogram, fontname = Helvetica]
  "EU Clinical Trials Register" 

  node [shape = rect, fontname = Helvetica]
  "Blogtrottr";"IFTT";"Other webservice"

  node [shape = circle, fixedsize = true, width = 0.9]
  "Email with updates";"Actions smartphone"

  # edge statements
  "EU Clinical Trials Register" -> "Blogtrottr"
  "EU Clinical Trials Register" -> "IFTT"
  "EU Clinical Trials Register" -> "Other webservice"

  "User sets up" -> "Blogtrottr"
  "User sets up" -> "IFTT"
  "User sets up" -> "Other webservice"

  "Blogtrottr" -> "Email with updates"
  "IFTT" -> "Actions smartphone"
  "Other webservice" -> "Email with updates"

}
')




```

# Step by step

## Notification by email



## Notification in a browser



## Notification using general systems 

Here the approach using IFTTT will be described. 

# Comments on this document

Comments and queries concerning this how-to are welcome. Please click here ()[] and search for an issue or open a new issue. The author will be automatically informed. 

End. 





