---
title: "How to obtain personalised updates from EU Clinical Trials Register"
author: "Ralf Herold"
date: "`r file.info('howto.Rmd')$mtime`"
output: html_document
params: 
  output_dir = "`r getwd ()`"

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# Objective

The purpose of this document is to describe how a user can set up personalised notifications to obtain updates on clinical trials of interest. This is based on protocol-related information that is made publicly available in the EU Clinical Trials Register [EUCTR](https://www.clinicaltrialsregister.eu/). The licence of this document (Apache 2.0) can be found [here](https://github.com/rfhb/euctrnotifications/blob/master/LICENSE).

```{r cars}
summary(cars)
```

# Overview

Also diagrammes will be included into the how to. 

```{r overviewdiagram, fig.height=10}
suppressWarnings({
  library(DiagrammeR, verbose = FALSE)
})

grViz('
digraph overview {
  # this does not follow a particular 
  # graphic methodology but just 
  # collects the elements 

  graph [overlap = true, fontsize = 10]

  node [shape = parallelogram, fontname = Helvetica]
  "EU Clinical Trials Register" 

  node [shape = rect, fontname = Helvetica]
  "Blogtrottr";"IFTT";"Other webservice"

  node [shape = circle, fixedsize = true, width = 0.9]
  "Email with updates";"Actions smartphone"

  # edge statements
  "EU Clinical Trials Register" -> "Blogtrottr"
  "EU Clinical Trials Register" -> "IFTT"
  "EU Clinical Trials Register" -> "Other webservice"

  "User sets up" -> "Blogtrottr"
  "User sets up" -> "IFTT"
  "User sets up" -> "Other webservice"

  "Blogtrottr" -> "Email with updates"
  "IFTT" -> "Actions smartphone"
  "Other webservice" -> "Email with updates"

}
')


# mermaid("
# graph LR
# A(EU Clinical Trials Register)-->B[Rectangular]
# A-->C{A Rhombus}
# C---D[Rectangle One]
# C-->E[Rectangle Two]
# ")






# grViz("
# digraph boxes_and_circles {
# 
#   # a 'graph' statement
#   graph [overlap = true, fontsize = 10]
# 
#   # several 'node' statements
#   node [shape = box,
#         fontname = Helvetica]
#   A; B; C; D; E; F
# 
#   node [shape = circle,
#         fixedsize = true,
#         width = 0.9] // sets as circles
#   1; 2; 3; 4; 5; 6; 7; 8
# 
#   # several 'edge' statements
#   A->1 B->2 B->3 B->4 C->A
#   1->D E->A 2->4 1->5 1->F
#   E->6 4->6 5->7 6->7 3->8
# }
# ")


```

# Step by step

## Notification by email



## Notification in a browser



## Notification using general systems 

Here the approach using IFTTT will be described. 

# Comments on this document

Comments and queries concerning this how-to are welcome. Please click here ()[] and search for an issue or open a new issue. The author will be automatically informed. 

End. 





