---
title: "How to obtain personalised updates from EU Clinical Trials Register"
author: "Ralf Herold"
date: "`r file.info('howto.Rmd')$mtime`"
output: html_document
params: 
  output_dir = "`r getwd ()`"

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
# command line set up:
# git remote add origin https://github.com/rfhb/euctrnotifications.git
# git pull -u origin master
# git push -u origin master
```

# Objective

The purpose of this document is to describe how a user can set up personalised notifications to obtain updates on clinical trials of interest. This is based on protocol-related information that is made publicly available in the EU Clinical Trials Register [EUCTR](https://www.clinicaltrialsregister.eu/). The licence of this document (Apache 2.0) can be found [here](https://github.com/rfhb/euctrnotifications/blob/master/LICENSE).

```{r cars}
summary(cars)
```

# Overview

Also diagrammes will be included into the how to. 

```{r overviewdiagram, fig.height=10}
suppressWarnings({
  library(DiagrammeR, verbose = FALSE)
})

grViz('
digraph overview {
  # this does not follow a particular 
  # graphic methodology but just 
  # collects the elements 

  graph [overlap = true]

  node [shape = parallelogram, fontname = Helvetica, fontsize = 12, fixedsize = true, height = 1, width = 2]
    euctr [label = "EU Clinical\nTrials Register"]

  node [shape = rect, fontname = Helvetica, fontsize = 12, fixedsize = true, height = 1, width = 1]
    bt    [label = "Blogtrottr"]
    iftt  [label = "IFTT"]
    other [label = "Other\nwebservice"]

  node [shape = circle, fontname = Helvetica, fontsize = 12, fixedsize = true, height = 1, width = 1]
    email  [label = "Email with\nupdates"]
    action [label = "Actions on\nsmartphone"]
    page   [label = "Personalised\nwebpage"]
    outp   [label = "Other\noutput"]
    query  [label = "User once finds\nrelevant trials"]

  # edge statements
   query -> euctr

   euctr -> bt
   euctr -> iftt
   euctr -> other
   euctr -> page

   bt    -> email
   iftt  -> action
   other -> outp

}
')

```

# Setting up notifications - step by step

## 1. User once defines relevant trials

## 2.a. Email with updates

## 2.b. Actions on smartphone

Here the approach using IFTTT will be described. 

## 2.c. Personalised webpage

# Comments on this document

Comments and queries concerning this how-to are welcome. Please click [here](https://github.com/rfhb/euctrnotifications/issues), where you can search for an issue or open a new issue. The author will be automatically informed. 

End.

